### 2019-12-29 README.Rmd
update README and pkgdown

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotempcv.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotempcv)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotempcv)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotempcv.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Build Status](https://img.shields.io/travis/mlr-org/mlr3spatiotempcv/master?label=Linux&logo=travis&style=flat-square)](https://travis-ci.org/mlr-org/mlr3spatiotempcv)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->
